\pagestyle{empty}
\section*{Резюме}\label{sec:cw-ru}\indent

Васильков Владимир Юрьевич

Разработка комплекса приложений "Оптовая торговля”

\pageref{LastPage} страниц, \TotalValue{totalfigures} рисунков, \TotalValue{additionCounter} приложений, \TotalValue{totallistings} листингов, \TotalValue{biblioCounter} использованных источников литературы.

Ключевые слова: сервер, интернет-магазин, мобильное приложение, веб-приложение, язык программирования Kotlin, \hyperlink{gloss:rest}{REST-архитектура}, 
контроль доступа, клиент-серверная архитектура, Spring Boot, JSON, веб-клиент, язык программирования TypeScript, Angular, HTML, CSS, Android-клиент, 
Android, MVVM, MVC, Clean Architecture, Android Architecture Components, базы данных.

Цель дипломной работы – проектирование и разработка клиент-серверных приложений взаимодействующих посредством \hyperlink{gloss:rest}{REST-принципа}.

Задача дипломной работы – реализовать комплекс приложений, способных взаимодействовать между собой, 
позволяющий управлять данными, которые содержатся в базе данных, контролировать доступ и привилегии пользователей, 
состоящий из серверного приложениями и нескольких клиентских приложений использующих разные платформы.

Объектом исследования выступают \hyperlink{gloss:rest}{REST-приложения}, построенные по принципу клиент-сервер.

Предмет исследования – основные функции и принципы функционирования клиент-серверных приложений, использующих \hyperlink{gloss:rest}{REST-подход} для взаимодействия клиента и сервера.

\section*{Summary}\label{sec:cw-eng}\indent

Uladzimir Vasilkou Yurievich

Development of set of applications "Wholesale online store"

\pageref{LastPage} pages, \TotalValue{totalfigures} images, \TotalValue{additionCounter} extensions, \TotalValue{totallistings} listings, \TotalValue{biblioCounter} bibliography sources.

Keywords: server, online store, mobile application, web-application, Kotlin programming language, \hyperlink{gloss:rest}{REST-architecture}, 
access control, client-server architecture, Spring Boot, JSON, web-client, TypeScript programming language, Angular, HTML, CSS, Android-client, 
Android, MVVM, MVC, Clean Architecture, Android Architecture Components, databases.

The purpose of the graduate work is investigation and research methods of implementation client-server application systems that interact with the help of \hyperlink{gloss:rest}{REST-principle}.

The aim of the graduate work is to implement application set, that can interact with each other, 
control data, that are stored in database, control access and user's privileges, 
that contains server application and few client applications that are uses different platforms.

The object of reserch is \hyperlink{gloss:rest}{REST-application}, that interact with the help of client-server principle.

The research subject is the main function and principles functioning client-server applications that uses \hyperlink{gloss:rest}{REST} way of interruction between client and server.